% This is an example of conditional compilation: it generates two
% flavours of curriculum vitae based on the command-line arguments.
% Use whatever you want instead of lualatex.
%
% lualatex fausto.en.tex
%
%   This will generate fausto.en.pdf with a generic curriculum
%   vitae.
%
% lualatex --jobname=fausto.ngo.en fausto.en.tex
%
%   This will generate fausto.ngo.en.pdf with a curriculum vitae
%   specific for NGO. Notice that portions of the original document
%   have been disabled while other portions have been enabled.

\documentclass{tccv}
\usepackage[english]{babel}


% The \personal box is put on the left column in fausto.ngo.en and
% on the right column in fausto.en for mere aesthetic purpose.
% Instead of copy&paste the data, defining it here as \PERSONAL
% macro to avoid repetition: only \PERSONAL will be carried around.
\newcommand\PERSONAL{%
    \personal
	{via Milano, 57\newline 25038 -- Rovato (BS)}
	{+39 (334) 8977107}
	{apalonyakori@gmail.com}}


\begin{document}

\part{Fausto Conter}

\ifjob{fausto.ngo.en}{\PERSONAL}{}

\section{Work experience}

\begin{eventlist}

\item{January 2011 -- May 2012}
     {Trutorq Italia, Rovato}
     {After-sale service and maintainer}

Assembly and automation of linear and heavy-duty actuators.
Planning and drawing of samples on 3D cad. Technical assistance for the
after-sale departement.

\ifjob{fausto.ngo.en}{
    \item{July 2010}
	 {\textsc{S.V.I.}, Mozambique}
	 {Consultant}

    Feasibility assessment for agriculture/food security proposal for
    Servizio Volontario Internazionale NGO in Mocodoene for a new project
    financed by Regione Lombardia.
}{}

\item{February 2010 -- August 2010}
     {\textsc{S.V.I.}, Zambia}
     {\large{1\textsuperscript{st}} consultant}

Providing agricultural and agroforestry skills at rural community in Solwezi for
the Servizio Volontario Internazionale NGO.

\ifjob{fausto.ngo.en}{
    \item{March 2007}
	 {\textsc{S.V.I.}, Uganda}
	 {Consultant}

    Collection of data with problem solving methodology for an assessment in
    Morulem for a new project financed by the Italian Ministry of Foreign
    Affairs.

    \item{June 2007 -- June 2009}
	 {S.V.I.,Uganda}
	 {Project Manager}

    The project included training courses of local people on agricultural,
    agroforestry and activities related to food security, beekeeping, animal
    traction and microcredit. The building of some zero grazing kraals and
    of one laboratory for honey and milk processing has been performed.
    Introduced cross breed program concerning cows and goats. Keeping
    microcredit and project accountability.
}{}

\item{November 2004 -- June 2009}
     {\textsc{S.V.I.}, Uganda}
     {Project Manager}

Providing agricultural and agroforestry skills at rural community in
Karamoja, northern Uganda, for the Servizio Volontario Internazionale
NGO. In the last year I have collected and organized
information for the SVI book \textit{African sprouts} that speaks about
the impact of agroforestry in Karamoja in the last 10 years. The job
consisted mainly in sampling and handling GPS data.
The project has been financed by many donors such as FAO, KPIU, CEI, WFP
and ISP.

\item{June 2001 -- August 2004}
     {Metecnal S.R.L., Rovato}
     {Technical quality control}

Controlling part dimensions, here included programming 3D CNC control
machine D.E.A. and drawing management. Helped the emprise in getting the
ISO 9002:1994 certification.

\ifjob{fausto.en}{
    \item{September 2000 -- May 2001}
	 {\textsc{Amica chips} s.r.l., Ospitaletto}
	 {Warehouseman}

    Good preparation and packaging before the delivering of food supplies
    for bars and restaurants.
}{}

\item{September 1995 -- August 2000}
     {Meccanica Artigiana S.R.L., Rovato}
     {Precision mechanical workshop}

Manufacturing parts on a metalwork lathe, here included tools presetting and
CNC programming.

\end{eventlist}

\ifjob{fausto.ngo.en}{}{\PERSONAL}

\section{Education}

\begin{yearlist}

\ifjob{fausto.ngo.en}{}{
    \item{2011}
	 {Autocad Inventor course}
	 {Autocad school, Brescia}
}

\item{2004}
     {Advanced course of english}
     {Anglican Kenian School, Nairobi}

\ifjob{fausto.ngo.en}{
    \item{2002 -- 2004}
	 {Course on problem solving}
	 {SVI headquarter, Brescia}
}{}

\ifjob{fausto.ngo.en}{}{
    \item{2001}
	 {Course on 3D programming}
	 {Technical school of Acer, Torino}
}

\item{1998 -- 2000}
     {Basic english course}
     {English school, Rovato}

\item{1995 -- 1998}
     {Technical drawing}
     {Scuola arte e mestieri, Brescia}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Italian}   {Native speaker}
\item{English}   {Oral: good -- Written: good}
\item{Karimojong}{Oral: good}
\item{French}    {Oral and written: basic}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Intermediate}
     {Microsoft office, Open office, Windows, Linux}

\item{Basic level}
     {Autocad, Autocad inventor}

\end{factlist}

\end{document}
